%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\usepackage{tipa}
\usepackage{upquote}

\usepackage{chronosys}

\usepackage{amssymb}

\newcommand{\colorsquare}[1]{\textcolor{#1}{$\blacksquare$}}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Mohammad-Ali ~A\textquotesingle{}R\^ABI\footnote{Officially (and ambiguously):\ Mohammad Ali ~ARABI.  Lastname:\ A'R\^ABI \textipa{[æPr6:bi]} means nomad.}}{29. 04. 1991 \ \ \ \ Tehran}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:aerabi.at.gmx.dot.de}{mohammad-ali\mbox{}@\mbox{}aerabi.com}\sbull
\textsmaller{+}49 176 3569 1988\sbull
% \textsmaller{+}31 6 301 59 402\sbull
\href{http://aerabi.github.io}{aerabi.github.io}\sbull 
% \href{http://www.linkedin.com/in/aerabi}{www.linkedin.com/in/aerabi} \sbull
\href{https://orcid.org/0000-0001-7088-417X}{\textsc{orc}i\textsc{d} 0000-0001-7088-417X} \\
% {\newnums angellandros} \emph{(Skype)}\sbull
Schildackerweg 8 \sbull
79115\thinspace\ {\sc Freiburg im Breisgau}\sbull
Baden-W\"urttemberg\sbull
{\sc Germany}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Timeline}


\startchronology[startyear=2009,startdate=false,stopdate=false]
\chronoperiode{2013}{2015}{MITRC}
\chronoperiode[color=brown]{2015}{2016}{CafeBazaar}
\chronoperiode{2017}{2018}{HiWi}
\chronoperiode[color=red]{2018}{2019}{Picnic}
\chronoperiode{2019}{2021}{AppTec}
\stopchronology

\startchronology[startyear=2009,startdate=false,stopdate=false]
\chronoperiode{2009}{2013}{BSc in Math}
\chronoperiode{2013}{2015}{MSc in Logic}
\chronoperiode{2016}{2021}{MSc in CS}
\stopchronology

\spacedhrule{-0.5em}{1em}

\roottitle{Professional Experience}

\headedsection
  {\href{https://www.apptec360.com/}{\colorsquare{yellow} AppTec Services GmbH}}
  {\textsc{Freiburg, Germany}} {%
  \headedsubsection
    {Senior Full-Stack Developer\footnote{All the positions are 100\% = full-time = 40 hrs/week if not otherwise specified.}}
    {Aug \apo19 -- Present}
    {\bodytext{Creating new backend with Node.js, TypeScript, and MongoDB. Coaching other developers. Setting up CI, Docker setup of the projects, package registries, etc. Doing interviews. \#RxJS \#GitLab}}
}

\headedsection
  {\href{https://picnic.app/}{\colorsquare{red} Picnic International BV}}
  {\textsc{Amsterdam, Netherlands}} {%
  \headedsubsection
    {Backend Java Developer}
    {Jun \apo18 -- Jul \apo19}
    {\bodytext{Implementing new features for the cross-product platform in Java 11. Fixing bugs and refactoring. Reviewing candidates' assignments. \#MongoDB \#RabbitMQ \#Docker \#RxJava}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.uni-freiburg.de/}{\colorsquare{cyan} Albert-Ludwigs-Universität Freiburg}}
  {\textsc{Freiburg im Breisgau, Germany}} {%
  \headedsubsection
    {Research Assistant / HiWi (50\%), \href{http://proglang.informatik.uni-freiburg.de}{Programming Languages Lab}}
    {Feb \apo17 -- Jul \apo18}
    {\bodytext{In charge of implementing a \href{https://mitpress.mit.edu/sites/default/files/titles/content/9780262162289_sch_0001.pdf}{linear lambda calculus} in Coq: \url{https://github.com/aerabi/llc}}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{https://en.wikipedia.org/wiki/Cafe_Bazaar}{\colorsquare{brown} Cafe Bazaar} (Officially:\ Âvây e Hamrâh e Hušmand e Hezârdastân)}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {Software Developer}
    {Aug \apo15 -- Sep \apo16}
    {\bodytext{Developing features on Divar (10th most used website in Iran) and CafeBazaar (Android app store). Creating CI pipelines. Developing tools for HR. \#Django \#PostgreSQL \#Docker \#GitLab-CI}}
}

\headedsection
  {\href{http://mitrc.ir}{\colorsquare{blue} Mobin Information Technology Research Center}}
  {\textsc{Tehran, Iran}} {%

  \headedsubsection
    {Java Developer}
    {Sep \apo13 -- Sep \apo15}
    {\bodytext{Creating a distributed platform based on Apache Storm and Hadoop in collaboration with the experts.}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to my \href{http://www.linkedin.com/in/angellandros}{Linked-in profile} for a more complete list of work experiences along with recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.uni-freiburg.de/}{\colorsquare{cyan} Albert-Ludwigs-Universität Freiburg}}
  {\textsc{Freiburg im Breisgau, Germany}} {%
  \headedsubsection
    {MSc in Computer Science (Informatik)}
    {2016 -- 2021}
    {\bodytext{Focused on Cyber-Physical Systems (as the specialization), Machine Learning (master project), and Programming Languages (master thesis).}}
}

\headedsection
  {\href{http://www.en.sharif.edu/}{\colorsquare{red} Sharif University of Technology}}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {MSc in Pure Mathematics / Logic \textnormal{\textit{~(discontinued)}}}
    {2013 -- 2015} 
    {\bodytext{Focused on Intuitionistic Logic and Proof Theory.
    Supervisor: Mohammad Ardeshir.\\
    Thesis: Categorial Grammar with Applications in Machine Translation.}}
}

\headedsection
  {\href{http://en.sbu.ac.ir/}{\colorsquare{blue} Shahid Beheshti University}}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {BSc in Pure Mathematics}
    {2009 -- 2013} 
    {\bodytext{Thesis: Distance Transform with Applications (in the fields of Digital Geometry).\\
    Two medals (bronze and silver) in National Collegiate Mathematics Competition (2011 and 2013), 5th team rank, and admission to International Mathematics Competition for University Students 2013.}}
}

\headedsection
  {\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{National Organization for Development of Exceptional Talents}}
  {\textsc{Karaj, Iran}} {%
  \headedsubsection
    {High-School Diploma \& Pre-University Degree in Mathematics and Physics}
    {2002 -- 2009} {}
}


% \spacedhrule{0.5em}{-0.4em}

% \roottitle{Skills}

% \inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
%   {Programming languages:}
%   {C \emph{(mother tongue)}, C++, Java, Python, Scala, JavaScript, TypeScript.}

% \vspace{0.5em}
% \inlineheadsection
%   {Natural languages:}
%   {Persian \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(working proficiency)}, Dutch \emph{(elementary proficiency)}. Lived in \textsc{Germany}, and \textsc{Netherlands},  \textsc{Switzerland}, and  \textsc{Iran}. Can read: Cyrillic, Hebrew, Greek, Phoenician, Old Persian Cuneiform, Avestan, and Pahlavi alphabets.}

% \vspace{0.5em}
% \inlineheadsection
%   {Other skills:}
%   {Create the most boring CV.~~Squash commits. Force push to master. Explain family relations between Mortal Kombat characters. Swear in Huttese. Watch Watchmen Ultimate Cut in one sitting.}

\end{document}

＀
