%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\usepackage{tipa}
\usepackage{upquote}

\usepackage{chronosys}

\usepackage{amssymb}

\newcommand{\colorsquare}[1]{\textcolor{#1}{$\blacksquare$}}

% colors
\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8} % sut
\definecolor{bazaar}{rgb}{0.6, 0.47, 0.48} % bazaar
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33} % sbu
\definecolor{camouflagegreen}{rgb}{0.47, 0.53, 0.42} % mitrc
\definecolor{carolinablue}{rgb}{0.6, 0.73, 0.89} % uni freiburg
\definecolor{frenchblue}{rgb}{0.0, 0.45, 0.73} % apptec

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Mohammad-Ali ~A\textquotesingle{}R\^ABI\footnote{Officially (and ambiguously):\ Mohammad Ali ~ARABI.  Lastname:\ A'R\^ABI \textipa{[æPr6:bi]} means nomad.}}{29. 04. 1991 \ \ \ \ Tehran}{Last update on \today~(v2.1.1)}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:aerabi.at.gmx.dot.de}{aerabi\mbox{}@\mbox{}gmx.de}\sbull
\textsmaller{+}49 176 3569 1988\sbull
% \textsmaller{+}31 6 301 59 402\sbull
\href{http://aerabi.com}{aerabi.com}\sbull 
\href{https://github.com/aerabi}{github.com/aerabi} \sbull
\href{http://www.linkedin.com/in/aerabi}{linkedin.com/in/aerabi} \sbull
% \href{https://orcid.org/0000-0001-7088-417X}{\textsc{orc}i\textsc{d} 0000-0001-7088-417X} \\
% {\newnums angellandros} \emph{(Skype)}\sbull
Schildackerweg 8 \sbull
79115\thinspace\ {\sc Freiburg im Breisgau}\sbull
Baden-W\"urttemberg\sbull
{\sc Germany}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

% \roottitle{Timeline}


% \startchronology[startyear=2009,startdate=false,stopdate=false,stopyear=2022]
% \chronoperiode[color=camouflagegreen]{2013}{2015}{MITRC}
% \chronoperiode[color=bazaar]{2015}{2016}{CafeBazaar}
% \chronoperiode[color=carolinablue]{2017}{2018}{HiWi}
% \chronoperiode[color=red]{2018}{2019}{Picnic}
% \chronoperiode[color=frenchblue]{2019}{2022}{AppTec}
% \stopchronology

% \startchronology[startyear=2009,startdate=false,stopdate=false,stopyear=2022]
% \chronoperiode[color=brickred]{2009}{2013}{BSc in Math}
% \chronoperiode[color=amethyst]{2013}{2015}{MSc in Logic}
% \chronoperiode[color=carolinablue]{2016}{2021}{MSc in CS}
% \stopchronology

% \spacedhrule{-0.5em}{1em}

\roottitle{Summary}

\begin{itemize}
    \item At least \textbf{6} years of 9-to-5 professional experience:
      \colorsquare{frenchblue} 2.5y +
      \colorsquare{red} 1y +
      \colorsquare{bazaar} 1.5y +
      \colorsquare{camouflagegreen} (2y $\times$ 60\%) \\
        using various languages: imperative, declarative, OO, functional, you name it.
    
    \item Extensive non-9-to-5 experience since \textbf{2004}, \textit{e.g.}:
    award-winning games written in Unity3D and C++,
    NPM packages @ \href{https://www.npmjs.com/~aerabi}{\url{npmjs.com/~aerabi}}\footnote{Texts in dark blue are hyperlinks. Those include all of the URLs, the employer names, and school names.}, 3 Android apps on the store, e2e web apps in PHP+MySQL, \textit{etc}.
    
    \item Life-long-learner. Automation-freak. Challenge-hungry.
\end{itemize}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Selected Professional Experience}

\headedsection
  {\href{https://www.apptec360.com/}{\colorsquare{frenchblue} AppTec Services GmbH}}
  {\textsc{Freiburg, Germany}} {%
  \headedsubsection
    {Senior Full-Stack Developer\footnote{All the positions are 100\% = full-time = 40 hrs/week if not otherwise specified.}}
    {Aug \apo19 -- Present}
    {\bodytext{Introduce a new backend in Node.js, TypeScript, and MongoDB, and a new frontend in Angular to replace the Zend framework legacy code. Introduce git, GitLab, Docker, RxJS, CI, local NPM registries. Introduce REST API, TDD, code reviews, dozens of CI jobs, hiring processes like code challenges. Develop compliance and escalation. Develop a type system with semantics. Manage a small team.}}
}

\headedsection
  {\href{https://picnic.app/}{\colorsquare{red} Picnic International BV}}
  {\textsc{Amsterdam, Netherlands}} {%
  \headedsubsection
    {Backend Java Developer}
    {Jun \apo18 -- Jul \apo19}
    {\bodytext{Implement new features for the cross-product platform team in Java 11. Fix bugs. Refactor. Review candidates' assignments. Do live database migrations. \#MongoDB \#RabbitMQ \#Docker \#RxJava}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{https://en.wikipedia.org/wiki/Cafe_Bazaar}{\colorsquare{bazaar} Cafe Bazaar} (aka Hezârdastân)}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {Backend Python Developer}
    {Aug \apo15 -- Sep \apo16}
    {\bodytext{Develop features on \href{https://en.wikipedia.org/wiki/Divar_(website)}{Divar} (10th most used website in Iran) and CafeBazaar (Android app store). Creat CI pipelines. Develop tools for HR. Organize Hackathons and Tech-Talks. Create educational onboarding videos. Do Scala and linguistics workshops. \#Django \#PostgreSQL \#Docker \#GitLab-CI}}
}

\headedsection
  {\colorsquare{camouflagegreen} Mobin IT Research Center}
  {\textsc{Tehran, Iran}} {%

  \headedsubsection
    {Java Developer (60\%)}
    {Sep \apo13 -- Sep \apo15}
    {\bodytext{Creat a distributed platform based on Apache Storm and Hadoop for real-time machine learning. Integrate the work of data scientists into the platform. \#ZooKeeper \#PostgreSQL \#Lucene \#Java7}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to my \href{http://www.linkedin.com/in/aerabi}{LinkedIn profile} for a more complete list of work experiences along with recommendations and certificates.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.uni-freiburg.de/}{\colorsquare{carolinablue} Albert-Ludwigs-Universität Freiburg}}
  {\textsc{Freiburg im Breisgau, Germany}} {%
  \headedsubsection
    {MSc in Computer Science (Informatik)}
    {2016 -- 2021}
    {\bodytext{Thesis: A Basis for Event-Driven Programming.}}
}

\headedsection
  {\href{http://www.en.sharif.edu/}{\colorsquare{amethyst} Sharif University of Technology}}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {MSc in Pure Mathematics / Logic \textnormal{\textit{~(discontinued)}}}
    {2013 -- 2015} 
    {\bodytext{Thesis: Categorial Grammar with Applications in Machine Translation.}}
}

\headedsection
  {\href{http://en.sbu.ac.ir/}{\colorsquare{brickred} Shahid Beheshti University}}
  {\textsc{Tehran, Iran}} {%
  \headedsubsection
    {BSc in Pure Mathematics}
    {2009 -- 2013} 
    {
    % \bodytext{Thesis: Distance Transform with Applications (in the fields of Digital Geometry).\\
    % Two medals (bronze and silver) in National Collegiate Mathematics Competition (2011 and 2013), 5th team rank, and admission to International Mathematics Competition for University Students 2013.}
    }
}

% \headedsection
%   {\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{National Organization for Development of Exceptional Talents}}
%   {\textsc{Karaj, Iran}} {%
%   \headedsubsection
%     {High-School Diploma \& Pre-University Degree in Mathematics and Physics}
%     {2002 -- 2009} {}
% }


\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Programming languages:}
  {C \emph{(mother tongue)}, C++, Java, Python, Scala, JavaScript, TypeScript.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Persian \emph{(mother tongue)}, English \emph{(C1--C2)}, German \emph{(B1)}, Dutch \emph{(A1--A2)}. 
%   Lived in \textsc{Germany}, and \textsc{Netherlands},  \textsc{Switzerland}, and  \textsc{Iran}. Can read: Cyrillic, Hebrew, Greek, Phoenician, Old Persian Cuneiform, Avestan, and Pahlavi alphabets.
  }

\vspace{0.5em}
\inlineheadsection
  {Other skills:}
  {Create the most boring CV.~~Squash commits. Force push to master. Explain family relations between Mortal Kombat characters. Swear in Huttese. Watch Watchmen Ultimate Cut in one sitting.}

\end{document}

＀
